\documentclass[11pt,letterpaper]{article}

% ── Geometry ──────────────────────────────────────────────────────────────────
\usepackage[margin=1in]{geometry}

% ── Pagination ────────────────────────────────────────────────────────────────
\usepackage[all]{nowidow}    % Require ≥2 lines on each side of a page break
\brokenpenalty=10000         % No hyphenated words across page breaks
\raggedbottom                % Allow uneven page bottoms rather than stretching

% ── Fonts ─────────────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage{newpxtext}     % Palatino-based serif (TeX Gyre Pagella)
\usepackage{newpxmath}     % Matching math font

% ── Colors ────────────────────────────────────────────────────────────────────
\usepackage[dvipsnames]{xcolor}
\definecolor{SectionBlue}{HTML}{1B3A5C}
\definecolor{AccentGray}{HTML}{4A4A4A}
\definecolor{QuoteBorder}{HTML}{8B9DAF}
\definecolor{RiskRed}{HTML}{C0392B}
\definecolor{RiskAmber}{HTML}{E67E22}
\definecolor{RiskGreen}{HTML}{27AE60}
\definecolor{BoxBg}{HTML}{F7F8FA}

% ── Tables ────────────────────────────────────────────────────────────────────
\usepackage{booktabs}
\usepackage{tabularx}

% ── Boxes ─────────────────────────────────────────────────────────────────────
\usepackage[framemethod=tikz]{mdframed}

% ── Lists ─────────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{needspace}

% ── Bibliography ─────────────────────────────────────────────────────────────
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\addbibresource{prfaq.bib}
\setcounter{biburllcpenalty}{7000}
\setcounter{biburlucpenalty}{8000}

% ── Hyperlinks ────────────────────────────────────────────────────────────────
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=SectionBlue,
  urlcolor=SectionBlue,
  citecolor=SectionBlue,
  pdfauthor={JM Freeman},
  pdftitle={Quarry --- PR/FAQ},
  pdfsubject={Working Backwards --- Product Discovery},
}

% ── Section styling ───────────────────────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\section}
  {\needspace{6\baselineskip}\Large\bfseries\color{SectionBlue}}
  {}
  {0pt}
  {}

\titleformat{\subsection}
  {\needspace{5\baselineskip}\large\bfseries\color{AccentGray}}
  {}
  {0pt}
  {}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{AccentGray}}
  {}
  {0pt}
  {}
\titlespacing*{\subsubsection}{0pt}{1em}{0.5em}[0pt]

% ══════════════════════════════════════════════════════════════════════════════
% Custom environments
% ══════════════════════════════════════════════════════════════════════════════

% ── \prsection{title} — styled press release section header ──────────────────
\newcommand{\prsection}[1]{%
  \vspace{1em}%
  {\large\bfseries\color{SectionBlue}#1}%
  \vspace{0.3em}\par%
}

% ── customerquote — indented, italic customer quote ──────────────────────────
\newmdenv[
  topline=false,
  bottomline=false,
  rightline=false,
  linewidth=3pt,
  linecolor=QuoteBorder,
  backgroundcolor=BoxBg,
  innerleftmargin=12pt,
  innerrightmargin=12pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  skipabove=\baselineskip,
  skipbelow=\baselineskip,
]{customerquote}

% ── spokespersonquote — indented spokesperson quote ──────────────────────────
\newmdenv[
  topline=false,
  bottomline=false,
  rightline=false,
  linewidth=3pt,
  linecolor=SectionBlue,
  backgroundcolor=BoxBg,
  innerleftmargin=12pt,
  innerrightmargin=12pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  skipabove=\baselineskip,
  skipbelow=\baselineskip,
]{spokespersonquote}

% ── faqpair — numbered Q&A pair with bold question ─────────────────────────
\newcounter{faqnum}
\newenvironment{faqpair}[1]{%
  \needspace{4\baselineskip}%
  \vspace{0.5em}%
  \refstepcounter{faqnum}%
  \noindent\textbf{\color{SectionBlue}Q\thefaqnum: #1}\par\nopagebreak[4]%
  \vspace{0.2em}%
  \begin{adjustwidth}{1em}{0pt}%
  \setlength{\parindent}{0pt}%
}{%
  \end{adjustwidth}%
  \vspace{0.5em}%
}
% ── \faqref{faq:slug} — clickable "FAQ 3" reference ──────────────────────────
\newcommand{\faqref}[1]{\hyperref[#1]{FAQ~\ref*{#1}}}

% ── \featureitem — numbered, referenceable feature entry ──────────────────────
\newcounter{featurenum}
\newcommand{\featureitem}[2]{%
  \refstepcounter{featurenum}%
  \item[\textbf{\color{SectionBlue}F\thefeaturenum.}]%
  \textbf{#1} --- #2%
}
\newcommand{\featureref}[1]{\hyperref[#1]{Feature~\ref*{#1}}}

% ── adjustwidth (for faqpair indentation) ────────────────────────────────────
\usepackage{changepage}

% ── Document stage ───────────────────────────────────────────────────────────
\newcommand{\prfaqstage}[1]{\def\theprfaqstage{#1}}
\prfaqstage{hypothesis}

% ── Document version ─────────────────────────────────────────────────────────
\newcommand{\prfaqversion}[2]{\def\theprfaqmajor{#1}\def\theprfaqminor{#2}}
\prfaqversion{4}{0}

% ── Header/footer ────────────────────────────────────────────────────────────
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize\textcolor{AccentGray}{Stage: \theprfaqstage{} \enspace\textbar\enspace v\theprfaqmajor.\theprfaqminor}}
\fancyhead[R]{\footnotesize\textcolor{AccentGray}{\thepage}}
\renewcommand{\headrulewidth}{0pt}

% ══════════════════════════════════════════════════════════════════════════════
% Document
% ══════════════════════════════════════════════════════════════════════════════

\begin{document}

% ── Headline block ───────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{SectionBlue}
    Free Plugin Gives Claude Code Persistent Memory Across Sessions} \\[0.8em]
  {\large\color{AccentGray}
    Quarry learns from every conversation and recalls what you've researched before---locally, with no cloud accounts or data leaving your machine} \\[0.3em]
  {\large\color{AccentGray}
    Open source plugin captures web research, session transcripts, and project files as searchable knowledge that compounds over time}
\end{center}

\vspace{0.5em}

% ══════════════════════════════════════════════════════════════════════════════
% PRESS RELEASE
% ══════════════════════════════════════════════════════════════════════════════

\section*{Press Release}

PORTLAND, OR --- September 2026 --- Today, Punt Labs announced Quarry, a free,
open-source tool that gives Claude persistent memory and instant access to
everything on your computer. Quarry indexes PDFs, scanned documents,
spreadsheets, presentations, web pages, notes, source code, and images---over
20 document formats---into a local semantic search engine, then exposes that
knowledge to Claude Code and Claude Desktop through the Model Context
Protocol~\cite{aitoolanalysis2026claudeplugins}. As a Claude Code plugin,
Quarry goes further: every web page Claude researches, every debugging
conclusion reached, every conversation transcript is automatically captured
before it can be lost to context compaction. Quarry runs entirely on the
developer's machine, is open source under the MIT license, and works with the
Claude Code plugin system that has grown to over 9{,}000 extensions
(see \faqref{faq:tam}).

\prsection{Problem}

Developers who use Claude Code for serious, multi-session work---refactoring
systems, debugging production issues, designing architectures---lose everything
they learn at the end of every conversation. A developer spends forty-five
minutes with Claude tracking down a connection timeout, reads three Stack
Overflow answers, identifies the root cause, and ships the fix. Two weeks later,
the same class of issue appears in a different service. Claude starts from
zero---searches the web again, reads the same answers, discovers the same root
cause. The developer recognizes the pattern but Claude does not.

People who use Claude for research, analysis, or writing hit the same wall.
They spend 5--15 minutes gathering context before they can ask their real
question. They upload PDFs to Projects. They copy-paste from old documents.
They point Claude Code at directories and hope the right files get picked up.
When the context window fills, they start over. A developer with ten years of
reference PDFs and design documents cannot make any of that knowledge available
to Claude without manually curating it first.

The knowledge is generated. The work is done. And then it vanishes
(see \faqref{faq:evidence}).

\prsection{Solution}

Quarry works at two levels: as a search engine for your files, and as a plugin
that captures knowledge automatically.

\textbf{Search engine.} Install with \texttt{uv tool install punt-quarry} and
\texttt{quarry install}. Point it at your
files---\texttt{quarry ingest report.pdf}, or register an entire directory with
\texttt{quarry register \texttildelow/Documents/research}. From that moment,
Claude can search your indexed knowledge by meaning rather than keywords. Every
format is handled automatically: text PDFs are extracted, scanned documents and
images are OCR'd locally, spreadsheets are serialized to preserve tabular
structure, presentations are split slide-by-slide, HTML pages are stripped of
boilerplate, and source code is parsed into semantic units.

\textbf{Ambient knowledge plugin.} As a Claude Code plugin, Quarry captures
knowledge passively through hooks. When Claude fetches a web page, a hook
queues the URL for background ingestion. Before context compaction, a hook
captures the conversation transcript. Your project directory is registered at
session start. Every hook is fail-open and non-blocking: you work normally, and
the knowledge base grows from the natural flow of every session. Per-project
configuration via \texttt{.punt-labs/quarry/config.md} lets you disable
individual hooks.

Because Quarry runs entirely on your machine, your documents never leave your
laptop. No cloud service, no API key, no subscription.

\prsection{Customer Quote}

\begin{customerquote}
\textit{``I've been using Claude Code full-time for seven months. The thing
that frustrated me most wasn't the model---it was the amnesia. I'd debug
something, figure out the fix, and three weeks later Claude would research the
same problem from scratch while I watched. With Quarry's hooks capturing web
pages from that first session, the second time Claude found the answer locally
in two seconds instead of spending five minutes searching Stack Overflow. After
a month, I had a searchable archive of every piece of research Claude had ever
done for me---and I never explicitly saved any of it.''}

\raggedleft --- \textbf{Sarah Lindqvist}, Staff Engineer at a Series C startup
\end{customerquote}

\prsection{Getting Started}

No accounts. No API keys. Under five minutes:

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Install:} {\small\texttt{uv tool install punt-quarry \&\& quarry install}}
        downloads the embedding model, installs the daemon, and configures
        Claude Code and Claude Desktop automatically.
  \item \textbf{Ingest:} \texttt{quarry register \texttildelow/Documents/work
        \&\& quarry sync} indexes an entire directory. Or ingest individual files
        with \texttt{quarry ingest report.pdf}.
  \item \textbf{Work normally.} Open Claude Code or Claude Desktop and ask a
        question. Claude calls Quarry's search tool automatically. The plugin
        hooks capture web research and session transcripts in the background.
\end{enumerate}

\prsection{Spokesperson Quote}

\begin{spokespersonquote}
``The bottleneck for LLM-assisted work isn't the model---it's the context. People
have years of accumulated knowledge on their hard drives, and none of it is
accessible to their LLM. We built Quarry to solve two problems: unlocking the
knowledge trapped in files, and preserving the knowledge generated during every
coding session that vanishes when the conversation ends. The Model Context
Protocol made the first possible; the Claude Code hook system made the second
possible. Quarry doesn't just index your files---it makes Claude itself
smarter.''

\raggedleft --- \textbf{JM Freeman}, Creator of Quarry
\end{spokespersonquote}

\prsection{Call to Action}

Quarry is available now at \url{https://pypi.org/project/punt-quarry/} and
\url{https://github.com/punt-labs/quarry}. It is free, open source (MIT
license), and always will be. Install with \texttt{uv tool install punt-quarry},
run \texttt{quarry install}, and start searching.

\newpage

% ══════════════════════════════════════════════════════════════════════════════
% FREQUENTLY ASKED QUESTIONS
% ══════════════════════════════════════════════════════════════════════════════

\section*{Frequently Asked Questions}

% ── External FAQs (Customer-facing) ──────────────────────────────────────────

\subsection*{External FAQs}

\begin{faqpair}{What is Quarry and who is it for?}\label{faq:what}
  Quarry is a local semantic search engine and Claude Code plugin that gives
  your coding sessions persistent memory. It indexes files across 20+ formats,
  captures web research and conversation transcripts automatically via hooks,
  and makes all of it searchable by meaning using hybrid search (vector + BM25
  fused via RRF). It is for developers who use Claude Code or Claude Desktop
  for multi-session work and are tired of Claude re-researching topics or
  manually uploading files before every session.
\end{faqpair}

\begin{faqpair}{How is this different from uploading files to Claude Projects?}\label{faq:vs-projects}
  Projects require you to select and upload files before every conversation, the
  context window limits how many you can include, and when you start a new
  conversation, you start from scratch. Quarry inverts this: index your files
  once, and Claude searches them on demand during any conversation. You don't
  decide what's relevant---Claude does. There is no context window limit because
  Quarry returns only the relevant passages, not entire files.
\end{faqpair}

\begin{faqpair}{How is this different from pointing Claude Code at a folder?}\label{faq:vs-folders}
  When Claude Code reads a directory, it reads files sequentially, consuming
  context window with every file it opens. For a folder with 50 documents, Claude
  Code may exhaust its context before finding the relevant passage. Quarry
  pre-indexes the content and returns only matching chunks, leaving the context
  window for reasoning rather than reading.
\end{faqpair}

\begin{faqpair}{How is this different from CLAUDE.md or memory files?}\label{faq:vs-claude-md}
  CLAUDE.md is static instructions that you write and maintain manually. It
  tells Claude \emph{how} to behave. Quarry captures \emph{what Claude
  learned}---web pages, debugging conclusions, design rationale---and makes it
  searchable by meaning. You do not write or maintain the knowledge base; it
  builds itself from every session. CLAUDE.md says ``use ruff for linting.''
  Quarry remembers that the last time you debugged a ruff configuration issue,
  the root cause was a conflicting pyproject.toml section, and the Stack
  Overflow answer that explained it.
\end{faqpair}

\begin{faqpair}{What file formats does Quarry support?}\label{faq:formats}
  PDF (both text and scanned/image pages), images (PNG, JPG, TIFF, BMP, WebP),
  spreadsheets (XLSX, CSV), presentations (PPTX), HTML, text files (Markdown,
  LaTeX, plain text, DOCX), and source code in 30+ languages parsed into
  semantic units via Tree-sitter AST. Every format is converted to text
  optimized for LLM consumption. Spreadsheets and presentation tables are
  serialized to LaTeX to preserve tabular structure. Source code is chunked by
  function and class boundaries, not arbitrary line counts. Scanned documents
  and images are OCR'd locally---no cloud account needed.
\end{faqpair}

\begin{faqpair}{How does the ambient capture work?}\label{faq:how-it-works}
  Quarry uses Claude Code's hook system~\cite{claude-code-hooks}---the same
  event-driven architecture used by plugins like Entire.io for code provenance.
  Three hooks ship today:

  \begin{itemize}[leftmargin=1.5em, nosep]
    \item \textbf{Session start} --- auto-registers the project directory so
          new files are indexed on sync, and injects a knowledge base summary
          into Claude's context.
    \item \textbf{Post web fetch} --- every URL Claude fetches is auto-ingested
          into the knowledge base for later semantic search.
    \item \textbf{Pre-compact} --- conversation transcript is captured before
          context compaction, preserving decisions and discoveries that would
          otherwise be lost.
  \end{itemize}

  All hooks write to a local staging directory and return
  immediately---they never block the conversation. A background process handles
  embedding and indexing. The hooks are fail-open: if Quarry is unavailable,
  Claude Code works exactly as before. Per-project configuration via
  \texttt{.punt-labs/quarry/config.md} lets you selectively disable individual
  hooks.
\end{faqpair}

\begin{faqpair}{Does my data leave my computer?}\label{faq:privacy}
  No. Quarry runs entirely on your machine. The vector database (LanceDB), the
  embedding model (snowflake-arctic-embed-m-v1.5 via ONNX Runtime), the OCR
  engine (RapidOCR), and all hooks execute locally. No data is sent to any
  cloud service. Captured web pages are re-fetched and stored locally, not
  forwarded through a proxy.
\end{faqpair}

\begin{faqpair}{How much does it cost?}\label{faq:cost}
  Free. Quarry is open source under the MIT license. There is no paid tier, no
  usage limits, and no telemetry. The embedding model download is approximately
  120\,MB (INT8 quantized); after that, everything runs offline.
\end{faqpair}

\begin{faqpair}{Can I use Quarry with tools other than Claude?}\label{faq:other-tools}
  Quarry exposes a standard MCP server over stdio and an HTTP API with
  WebSocket support. Any MCP-compatible client can use it. Today that includes
  Claude Code and Claude Desktop. As other LLM tools adopt MCP, Quarry will
  work with them without modification. The CLI also works standalone for
  direct search without any LLM.
\end{faqpair}

\begin{faqpair}{How does search quality compare to keyword search (Spotlight, grep)?}\label{faq:search-quality}
  Quarry uses hybrid search: vector similarity for meaning and BM25 full-text
  for keyword precision, fused via reciprocal rank fusion (RRF). Searching for
  ``authentication logic'' finds a function called \texttt{verify\_credentials}
  even though the words don't overlap (vector match), and searching for a
  specific error code finds the exact line (BM25 match). You get both semantic
  understanding and keyword exactness in a single query, running locally with a
  768-dimension embedding model and Tantivy full-text index.
\end{faqpair}

\begin{faqpair}{Do I have to manually index everything?}\label{faq:passive-capture}
  No. The Claude Code plugin captures knowledge passively through three
  hooks~\cite{claude-code-hooks} (see \faqref{faq:how-it-works} for detail).
  You work normally; the knowledge base grows in the background. Explicit CLI
  commands are available for one-off ingestion.
\end{faqpair}

% ── Internal FAQs (Business-facing) ──────────────────────────────────────────

\newpage
\subsection*{Internal FAQs}

\subsubsection*{Value \& Market}

\begin{faqpair}{What is the total addressable market?}\label{faq:tam}
  Claude Code had over 115{,}000 developers by mid-2025~\cite{ppcland2025claudecode115k},
  with Anthropic reporting doubled weekly active users and annualized revenue
  exceeding \$2.5B by early 2026~\cite{anthropic2026seriesg}. The plugin
  ecosystem grew from zero to 9{,}000+ extensions in under five
  months~\cite{startuphub2025claudeplugins}. The broader AI-assisted coding
  market (Cursor, GitHub Copilot, Windsurf) totals millions of developers.

  The target segment is \emph{multi-session power users}---developers doing
  complex work spanning days or weeks. The Qodo survey found 41--52\% of
  developers report context-related frustration~\cite{qodo2025aicodequality}.
  A quarter of frustrated Claude Code users is tens of thousands. Because
  Quarry is free, TAM is measured in adoption. Success means becoming the
  default way Claude Code sessions persist knowledge.
\end{faqpair}

\begin{faqpair}{What evidence do we have that developers want this?}\label{faq:evidence}
  Four categories of evidence:

  \textbf{Survey data:} The Qodo ``State of AI Code Quality'' survey found
  that context-related frustration affects 41--52\% of developers (increasing
  with seniority), and ``improved contextual understanding'' is the single
  most-requested AI improvement at 26\% of votes. The Stack Overflow 2025
  survey (49{,}000+ respondents) found 81\% have security/privacy concerns
  about AI data use~\cite{stackoverflow2025survey}---local-first architecture
  directly addresses this.

  \textbf{Market signal:} SageOx~\cite{sageox2026} positions itself as ``context
  infrastructure for human-agent collaboration.'' Entire.io, founded by former
  GitHub CEO Thomas Dohmke with \$60M in seed
  funding~\cite{techcrunch2026entirefunding}, captures the reasoning behind
  AI-generated code via a git shadow branch~\cite{entireio2026github}. Both
  companies are building for the same problem.

  \textbf{Behavioral:} Claude Code's own memory features (CLAUDE.md,
  auto-memory) are static and manually maintained---they capture instructions,
  not learned knowledge. The gap between ``remember my preferences'' and
  ``remember what we researched'' is the gap Quarry fills.

  \textbf{Adjacent:} Rewind/Limitless raised \$33M+, was acquired by Meta in
  December 2025, and shut down both its Pendant hardware and Rewind desktop
  app~\cite{techcrunch2025limitless,9to5mac2025rewindshutdown}. The demand was
  real; the cloud-dependent model was fragile. Quarry's local-first
  architecture is resilient to this failure mode.
\end{faqpair}

\begin{faqpair}{Who are the competitors and why will we win?}\label{faq:competitors}
  The competitive landscape splits into six categories; no single tool covers
  Quarry's niche. See the Competitive Landscape appendix for the full analysis.

  \textbf{MCP-native code search} (DeepContext, claude-context, mcp-local-rag,
  Chroma MCP): Code-only, typically require cloud API keys, no agent memory.
  Quarry indexes 20+ formats, runs fully offline, and provides agent memory with
  identity tagging and temporal decay.

  \textbf{Documentation servers} (Context7): Pre-indexed public library docs.
  Complementary, not competitive. Quarry indexes \emph{your} files; Context7
  indexes \emph{everyone's} libraries.

  \textbf{Personal knowledge bases} (Khoj, Obsidian plugins, Mem.ai):
  GUI-first, human-interactive, no MCP server, no agent memory concept.

  \textbf{Session capture} (Entire.io, SageOx, Screenpipe): Record what
  happened. Quarry adds semantic search---making captured knowledge retrievable
  by meaning across sessions.

  \textbf{RAG frameworks} (RAGFlow, AnythingLLM, LlamaIndex): Toolkits
  requiring assembly. Quarry is opinionated and zero-configuration.

  \textbf{IDE built-in indexing} (Cursor, Windsurf): Codebase search locked
  inside their editors, cloud-dependent, code-only, invisible to external agents.

  \textbf{Platform risk:} Anthropic building ambient memory natively into
  Claude Code is the most dangerous response. Quarry's residual value:
  (1)~cross-tool portability via MCP, CLI, and HTTP API; (2)~user-owned data in
  an open format (LanceDB); (3)~20+ format indexing; (4)~open source and
  auditable. Secondary risks: Cursor or Windsurf exposing indexes via MCP; Khoj
  shipping an MCP server; a vector DB vendor shipping a batteries-included
  search product.
\end{faqpair}

\begin{faqpair}{What is the user acquisition strategy?}\label{faq:acquisition}
  Quarry has no installed base yet. Acquisition depends on three channels:

  \textbf{PyPI:} Users searching for ``claude mcp,'' ``local RAG,'' or
  ``semantic search'' find Quarry on PyPI. The one-line install
  (\texttt{curl~\ldots~|~sh}) and zero-account setup reduce friction.

  \textbf{Claude Code plugin marketplace:} The marketplace is the primary
  discovery surface for Claude Code users. Quarry is listed and installable
  with one command.

  \textbf{GitHub and community:} Engineering quality (936 tests, strict typing,
  clean architecture) attracts contributors. Presence in Claude community
  forums and word-of-mouth among power users.

  The risk is obscurity (see \faqref{faq:failure}). No channel has proven
  traction yet.
\end{faqpair}

\subsubsection*{Technical}

\begin{faqpair}{What are the major technical risks?}\label{faq:tech-risks}
  \textbf{Embedding model quality (medium risk):} snowflake-arctic-embed-m-v1.5
  (768 dimensions, 512 token context) performs well for general text but may
  underperform on domain-specific content (medical, legal, financial jargon).
  Mitigation: the backend abstraction allows swapping models without code
  changes---a model upgrade is a configuration change, not an architecture change.

  \textbf{OCR accuracy on degraded scans (low risk):} RapidOCR produces
  good-enough text for semantic search but lower character accuracy than
  commercial OCR. Mitigation: semantic search is tolerant of OCR errors
  because it matches by meaning, not exact characters.

  \textbf{LanceDB scalability (low risk):} At tens of thousands of documents,
  query latency and index size may become concerns. Mitigation: the database
  abstraction allows migration to a different backend, and named databases allow
  partitioning by project.

  \textbf{Hook latency (low risk):} All hooks must return fast to avoid
  blocking Claude Code. The hooks write to files and return
  immediately---no embedding or network calls in the hook path. Cold start
  for the hook dispatcher is 0.24s (stdlib-only imports, no heavy
  dependencies).
\end{faqpair}

\begin{faqpair}{What dependencies exist on external systems?}\label{faq:dependencies}
  \textbf{MCP protocol:} Quarry depends on the MCP specification remaining
  stable and Claude clients continuing to support MCP tool servers. Risk is low:
  Anthropic is investing heavily in MCP, and multiple third-party clients now
  support it.

  \textbf{Claude Code hook system:} The ambient capture layer depends on Claude
  Code's hook events (PostToolUse, PreCompact, SessionStart) remaining stable.
  Risk is low: the hook system is actively developed and used by multiple
  shipping plugins~\cite{claude-code-hooks}.

  \textbf{Embedding model hosting:} The ONNX model is downloaded from Hugging
  Face Hub at install time. If removed, existing installations continue to work
  (model cached locally). Mitigation: model is pinned to a specific git revision.

  \textbf{Tree-sitter grammars:} Mature, widely-used open-source projects with
  low abandonment risk.

  Quarry operates fully offline after installation.
\end{faqpair}

\begin{faqpair}{What is the development timeline and current status?}\label{faq:timeline}
  Quarry is live on PyPI. Current capabilities:

  \textbf{Shipped (v1.10.1):} PDF ingestion (text + local OCR), image OCR,
  spreadsheet ingestion (XLSX/CSV), presentation ingestion (PPTX), HTML
  parsing, URL and sitemap crawling, text file parsing, DOCX, source code
  parsing (30+ languages via Tree-sitter), semantic search with metadata
  filtering, hybrid search (vector similarity + BM25 full-text fused via
  reciprocal rank fusion), agent memory with identity tagging and temporal
  decay (via ethos integration), directory sync with
  \texttt{.gitignore}/\texttt{.quarryignore} support, named databases and
  collections, MCP server with 10+ tools, CLI with \texttt{--version} and
  plain-text help, HTTP API with WebSocket MCP endpoint and Bearer token
  authentication, Claude Code plugin with three hooks (session start
  auto-registration, post web fetch auto-ingestion, pre-compact transcript
  preservation), daemon architecture (launchd/systemd) with mcp-proxy for
  shared-process MCP, ONNX provider auto-detection with CUDA/GPU acceleration
  (auto-installs \texttt{onnxruntime-gpu} on NVIDIA machines, uses FP16
  model), researcher subagent for combined local + web search, CLAUDE.md
  injection for agent discovery, ethos extension for per-identity session
  context. 936 automated tests, strict type checking (mypy + pyright).

  \textbf{Roadmap:} Remote server support (\texttt{quarry login/logout/remote}
  for LAN GPU sharing), knowledge recall system (session briefing, local-first
  search nudge), \texttt{quarry sync --watch} for live filesystem monitoring,
  PII detection and redaction, Google Drive connector.
\end{faqpair}

\begin{faqpair}{What is the scaling story?}\label{faq:scaling}
  Quarry is designed for personal-scale workloads: thousands to tens of
  thousands of documents on a single machine.

  On an M2 MacBook Air, the ONNX embedding model sustains \texttildelow11
  chunks/second. A 10{,}000-file directory (\texttildelow70{,}000 chunks)
  takes roughly 1.5--2 hours. Files are queryable as they are indexed.
  Subsequent syncs are incremental.

  Query latency is constant regardless of database size because LanceDB uses
  IVF-PQ indexing.

  Quarry does not target multi-user or server deployments. The one exception is
  the Fly.io deployment that serves the punt-labs.com chat widget's RAG backend.
\end{faqpair}

\begin{faqpair}{What happens as the knowledge base grows?}
  LanceDB is designed for datasets far larger than a personal knowledge base.
  Search latency remains sub-second up to millions of vectors; 10{,}000--50{,}000
  documents (years of heavy use) is well within range. Disk usage scales at
  approximately 1--5\,MB per 100 documents for embeddings and metadata.
  Captured content (web pages, transcripts) adds more but is bounded by dedup
  logic---the same URL is not re-ingested.

  \texttt{quarry delete} lets users prune old or low-value collections.
\end{faqpair}

\subsubsection*{Business}

\begin{faqpair}{What is the revenue model?}\label{faq:revenue}
  None. Value is measured in adoption and community contribution, not revenue.
\end{faqpair}

\begin{faqpair}{What are the key metrics for success?}\label{faq:metrics}
  \begin{itemize}[leftmargin=1.5em, nosep]
    \item \textbf{PyPI installs:} Monthly download count as a proxy for adoption.
          Current baseline: \texttildelow765 monthly downloads (March 2026).
          Tiered thresholds at 6 months: below 500/month triggers a go/no-go
          decision on continued development; 1{,}000/month indicates baseline
          adoption; 5{,}000/month indicates product-market fit.
    \item \textbf{GitHub stars:} Community interest signal.
          Target: 500 stars within 6 months; 2{,}000 indicates breakout.
    \item \textbf{Active MCP connections:} Users with Quarry configured in Claude
          Code or Desktop. Not directly measurable without telemetry; inferable
          from support requests and community engagement.
    \item \textbf{Contributor count:} External contributors submitting PRs.
          Target: 5+ contributors within the first year.
    \item \textbf{Format coverage:} PDF, images, text, code, XLSX, PPTX, HTML
          are all shipped. Remaining targets: EPUB, email (EML/MBOX), audio
          transcription.
  \end{itemize}
\end{faqpair}

\begin{faqpair}{Why now? What has changed?}\label{faq:why-now}
  Three shifts converged:

  \textbf{MCP maturity:} The Model Context Protocol shipped in late 2024 and is
  now supported by Claude Code and Claude Desktop. A local tool can be a native
  part of an LLM's reasoning process, not an external API the user invokes
  manually.

  \textbf{Claude Code plugin ecosystem:} The hook system (PostToolUse,
  PreToolUse, PreCompact, SessionStart) is stable and used by shipping
  plugins~\cite{claude-code-hooks}. The ecosystem grew to 9{,}000+ plugins in
  under five months~\cite{startuphub2025claudeplugins}. Quarry applies this
  infrastructure to knowledge persistence.

  \textbf{Local inference viability:} ONNX Runtime, quantized embedding models,
  and LanceDB make it feasible to run a complete semantic search pipeline on a
  laptop CPU in under a second per query. GPU acceleration is now zero-config:
  the installer auto-detects NVIDIA hardware and swaps in
  \texttt{onnxruntime-gpu} with FP16 models, giving the same tool a hardware
  fast path without user configuration.
\end{faqpair}

\begin{faqpair}{What are we not building?}\label{faq:not-building}
  \begin{itemize}[leftmargin=1.5em, nosep]
    \item \textbf{A cloud service.} Quarry will never require an account,
          subscription, or data upload. Local-first is a permanent design
          constraint, not a temporary limitation.
    \item \textbf{A multi-user platform.} Quarry supports remote access to a
          daemon on the local network (e.g.\ sharing a GPU machine), but this is
          single-user remote access with Bearer token auth, not a multi-tenant
          platform with user accounts, access control, or shared databases.
    \item \textbf{Media search.} Quarry does not find images by visual content
          or match audio. It extracts \emph{text} from every format and indexes
          the knowledge inside.
    \item \textbf{A note-taking app.} Quarry indexes existing files. It does not
          provide an editor, a tagging system, or a filing structure.
    \item \textbf{A general-purpose RAG framework.} No pipeline assembly, no
          pluggable retrievers, no chain-of-thought orchestration. Quarry is
          deliberately opinionated and zero-configuration.
    \item \textbf{Structured knowledge extraction.} Quarry indexes raw content
          and lets semantic search surface what is relevant. It does not extract
          summaries, decisions, or intent from captured content.
    \item \textbf{Code provenance tracking.} Quarry does not add metadata to
          git commits or link commits to sessions.
  \end{itemize}
\end{faqpair}

\begin{faqpair}{What does failure look like?}\label{faq:failure}
  Three plausible failure scenarios:

  \textbf{Obscurity:} Quarry ships, works well, and nobody discovers it. After
  6 months, monthly PyPI installs plateau below 200. \textit{Response:} The
  most likely failure mode. Mitigation: active presence in Claude community
  forums. If installs plateau, invest in content marketing before building more
  features.

  \textbf{First-party displacement:} Anthropic ships native file indexing or
  session memory in Claude Code. \textit{Response:} That validates the thesis.
  Quarry still serves users who need local-only indexing, offline access, or
  formats Anthropic doesn't cover.

  \textbf{Capture noise exceeds signal.} The knowledge base fills with
  low-value web pages and irrelevant transcript fragments, degrading search
  quality. \textit{Response:} Start conservative (web research + compaction
  only). If signal-to-noise is poor, add quality filtering---URL pattern
  exclusions, minimum page length, dedup by content similarity.
\end{faqpair}

\begin{faqpair}{What is the next step to validate adoption?}\label{faq:next-validation}
  Build the knowledge recall system: a session-start briefing that tells Claude
  what is in the knowledge base, and a pre-web-search nudge that suggests
  checking local knowledge first. Both hooks are read-only and fail-open. If
  the recall mechanism demonstrably reduces redundant web searches, the ambient
  capture hooks become more valuable. If not, the capture is still useful for
  manual search via \texttt{/find}.
\end{faqpair}

% ══════════════════════════════════════════════════════════════════════════════
% FOUR RISKS ASSESSMENT
% ══════════════════════════════════════════════════════════════════════════════

\newpage
\section*{Risk Assessment}

\renewcommand{\arraystretch}{1.6}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
\toprule
\textbf{\color{SectionBlue}Risk} & \textbf{\color{SectionBlue}Rating} & \textbf{\color{SectionBlue}Assessment} \\
\midrule
Value      & \textcolor{RiskAmber}{Medium} & Multiple startups and survey data validate the problem~\cite{qodo2025aicodequality,techcrunch2026entirefunding}. Discovery and activation are the primary risks---demand is proven but users must find Quarry and index enough content to experience the value. \\
Usability  & \textcolor{RiskAmber}{Medium} & For CLI-native users, three commands to value. Auto-configures MCP. No accounts, no API keys. The knowledge recall nudge---a planned interaction pattern between hooks and the model---has no reference class and will need validation. \\
Feasibility & \textcolor{RiskGreen}{Low} & The product is live on PyPI (v1.10.1) with 936 passing tests and strict type checking. Core pipeline, daemon architecture, plugin hooks, MCP server, hybrid search, agent memory, and CUDA acceleration are all shipped. Remaining roadmap items are additive features, not architectural risks. \\
Viability  & \textcolor{RiskGreen}{Low} & No revenue model to validate. Zero marginal cost (runs on user hardware). MIT license. \\
\bottomrule
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

\vspace{1em}

\textbf{Value risk} is the dominant concern. The thesis: local semantic search
combined with passive knowledge capture changes how developers work with AI
coding tools---your LLM has access to everything you know, and knowledge
generated during sessions compounds instead of evaporating. Discovery is the
immediate challenge: users must find Quarry and invest enough initial indexing
to experience Claude finding a document they forgot they had. The planned
recall system will test whether automatic surfacing of local knowledge changes
behavior; the capture hooks already deliver value for manual search.

% ══════════════════════════════════════════════════════════════════════════════
% FEATURE APPENDIX
% ══════════════════════════════════════════════════════════════════════════════

\newpage
\section*{Feature Appendix}

Defines scope. Features are categorized to prevent scope creep.

\subsection*{Core (Shipped)}

\begin{enumerate}[nosep,leftmargin=2.5em]
  \featureitem{Local semantic search}{Index local files and retrieve passages by meaning across 20+ document formats.}\label{feat:semantic-search}
  \featureitem{MCP server}{11 tools covering search, ingestion, management, and database operations. Exposes Quarry to Claude Code and Claude Desktop as a native tool.}\label{feat:mcp-server}
  \featureitem{Directory registration and sync}{Bulk ingestion workflow: register a directory once, sync incrementally as files change. Respects \texttt{.gitignore} and \texttt{.quarryignore}.}\label{feat:directory-sync}
  \featureitem{Local OCR}{Extract text from scanned documents and images on-device via RapidOCR with no cloud account required.}\label{feat:local-ocr}
  \featureitem{Named databases}{Separate knowledge bases by project or domain.}\label{feat:named-databases}
  \featureitem{One-command install}{\texttt{quarry install} auto-configures MCP for Claude Code and Claude Desktop, downloads mcp-proxy, and installs the daemon.}\label{feat:one-command-install}
  \featureitem{Claude Code plugin}{Plugin with three hooks: auto-register project directory on session start, auto-ingest URLs Claude fetches (post web fetch), and preserve conversation transcripts before context compaction (pre-compact). All hooks fail-open, non-blocking, per-project configurable.}\label{feat:claude-plugin}
  \featureitem{Daemon architecture}{Single background process (\texttt{quarry serve}) loads the embedding model once and serves all sessions via WebSocket MCP endpoint. Lightweight mcp-proxy binary bridges MCP stdio to the daemon, eliminating per-session Python startup.}\label{feat:daemon}
  \featureitem{Researcher agent}{Combines local Quarry search with web research. Searches locally first, fills gaps from the web, and auto-ingests findings so research compounds across sessions.}\label{feat:researcher}
  \featureitem{Hybrid search}{Vector similarity + BM25 full-text fused via RRF. Semantic understanding plus keyword precision.}\label{feat:hybrid-search}
  \featureitem{Agent memory}{Per-agent memory with identity tagging via ethos integration. Memory types (fact, observation, procedure, opinion) with temporal decay for relevance. Agents remember across sessions and machines.}\label{feat:agent-memory}
  \featureitem{CUDA/GPU acceleration}{Auto-detects NVIDIA hardware and uses FP16 model via CUDAExecutionProvider. Installer swaps \texttt{onnxruntime} for \texttt{onnxruntime-gpu} with rollback on failure.}\label{feat:cuda}
  \featureitem{HTTP API with authentication}{Bearer token on all endpoints except \texttt{/health}. Server refuses non-loopback binding without an API key. Enables secure LAN access to a GPU daemon.}\label{feat:http-auth}
  \featureitem{Ethos integration}{Injects per-identity agent personality, memory instructions, and team context into sessions automatically.}\label{feat:ethos}
\end{enumerate}

\subsection*{Should Do}

\begin{enumerate}[nosep,leftmargin=2.5em]
  \featureitem{Remote server support}{\texttt{quarry login/logout/remote} for connecting to a remote daemon (e.g.\ a LAN GPU machine). Credentials in OS keyring. Transparent MCP reconfiguration. Enables sharing a single GPU-accelerated instance.}\label{feat:remote}
  \featureitem{Knowledge recall system}{Session-start briefing and pre-web-search nudge surface relevant local knowledge before Claude searches the web.}\label{feat:knowledge-recall}
  \featureitem{Live filesystem monitoring}{\texttt{sync --watch} automatically re-indexes on file changes.}\label{feat:sync-watch}
  \featureitem{Google Drive connector}{Ingest cloud-hosted documents without manual download.}\label{feat:google-drive}
  \featureitem{PII detection and redaction}{Prevents sensitive personal information from entering the search index.}\label{feat:pii-redaction}
\end{enumerate}

\subsection*{Won't Do}

\begin{enumerate}[nosep,leftmargin=2.5em]
  \featureitem{Multi-user platform}{Remote daemon access for LAN GPU sharing is supported; multi-tenant accounts, access control, and shared databases are not.}\label{feat:no-multi-user}
  \featureitem{Media search by visual or audio content}{Quarry extracts text from every format. It does not match images by visual similarity or search audio.}\label{feat:no-media-search}
  \featureitem{Note-taking or filing system}{Indexes existing files. No editor, tagging, or organizational structure.}\label{feat:no-note-taking}
  \featureitem{General-purpose RAG framework}{Deliberately opinionated and zero-configuration. No pipeline assembly, no pluggable retrievers.}\label{feat:no-rag-framework}
  \featureitem{Hosted web UI}{Team browsing of shared knowledge is outside scope.}\label{feat:no-web-ui}
  \featureitem{Structured knowledge extraction}{Extraction is lossy and adds complexity. Semantic search over raw content is sufficient.}\label{feat:no-extraction}
  \featureitem{Git commit metadata}{Checkpoint trailers or session IDs in git commits are outside scope.}\label{feat:no-git-meta}
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
% COMPETITIVE LANDSCAPE
% ══════════════════════════════════════════════════════════════════════════════

\newpage
\section*{Competitive Landscape}

Surveyed March 2026. The landscape divides into six categories; no single tool
covers Quarry's niche.

\subsection*{MCP-Native Code Search}

Tools that index code and serve results to AI coding agents via MCP.

\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Tool} & \textbf{Differentiator} & \textbf{Weakness vs Quarry} \\
\midrule
DeepContext & AST-level symbol awareness, Jina reranking & Code-only (TS/Python). Cloud API key required. No agent memory. \\
claude-context (Zilliz) & VSCode extension, AST chunking & Two cloud API keys (Zilliz + OpenAI). Code-only. Not local-first. \\
mcp-local-rag & Zero setup, fully private & Early-stage. Limited formats. No hybrid RRF. No agent memory. \\
Chroma MCP & Mature vector DB ecosystem & BYO everything: no parsing, no chunking, no agent memory. A DB, not a product. \\
\bottomrule
\end{tabularx}

\subsection*{Documentation Servers}

Pre-indexed public library documentation for AI coding tools.

\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Tool} & \textbf{Differentiator} & \textbf{Weakness vs Quarry} \\
\midrule
Context7 (Upstash) & 9{,}000+ pre-indexed libraries. ``use context7'' trigger. & Public docs only. Cannot index local files. Cloud-only. Different problem. \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\textit{Assessment:} Complementary, not competitive. Context7 solves stale
training data for public APIs; Quarry solves local knowledge retrieval.
A ``use quarry'' trigger pattern is worth adopting (see beads backlog).

\subsection*{Personal Knowledge Bases}

AI-powered tools for indexing and searching personal documents.

\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Tool} & \textbf{Differentiator} & \textbf{Weakness vs Quarry} \\
\midrule
Khoj & Full AI assistant: chat, agents, automations. Multi-platform. & Heavy (Docker + PostgreSQL). No MCP. No CLI-first. Not for coding agents. \\
Mem.ai & Zero-effort AI auto-organization. Polished consumer UX. & Cloud-only. No MCP. Closed source. No developer focus. \\
Obsidian + Smart Connections & 786K+ downloads. Deep vault integration. & Obsidian-only. Markdown only. No MCP. No document format diversity. \\
AnythingLLM & Full AI workspace. Built-in LanceDB. GUI-first. & No MCP. Smaller embedding (384-dim). Broader scope dilutes search quality. \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\textit{Assessment:} These tools are GUI-first and human-interactive. Quarry is
CLI/MCP-first, designed for AI agents as the primary consumer. The risk is Khoj
shipping an MCP server---they have the breadth to compete directly.

\subsection*{Session Capture \& Activity Recording}

Tools that record developer sessions or screen activity.

\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Tool} & \textbf{Differentiator} & \textbf{Weakness vs Quarry} \\
\midrule
Entire.io & Git shadow branch for session metadata. \$60M seed. & Records what happened; no semantic search. Different abstraction. \\
SageOx & Hosted context platform for enterprise teams. & Enterprise SaaS. Quarry serves individuals with no accounts. \\
Screenpipe & 24/7 screen + audio capture. 16K+ GitHub stars. & Activity capture, not document search. No semantic search. No MCP. \\
Limitless (ex-Rewind) & Meeting capture with hardware pendant. & Acquired by Meta Dec 2025. Mac app shut down. Cloud-only. \\
\bottomrule
\end{tabularx}

\subsection*{RAG Frameworks}

Pipeline toolkits that require assembly to build a search product.

\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Tool} & \textbf{Differentiator} & \textbf{Weakness vs Quarry} \\
\midrule
RAGFlow & Enterprise-grade: visual agent builder, team collab. & Heavy (Docker + Elasticsearch). No MCP. No CLI-first UX. \\
LlamaIndex RAG CLI & Massive ecosystem. Composable. & Framework, not product. Typically needs OpenAI API. No MCP server. \\
\bottomrule
\end{tabularx}

\subsection*{IDE Built-in Indexing}

Codebase search locked inside specific editors.

\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Tool} & \textbf{Differentiator} & \textbf{Weakness vs Quarry} \\
\midrule
Cursor & Deep IDE integration. @Codebase, @Docs. Shared team indexes. & Locked ecosystem. Cloud embeddings (Turbopuffer). Code-only. No MCP. \\
Windsurf & Cascade auto-indexes. Remote indexing for 1M+ line repos. & IDE-only. Not accessible to external agents. No document search. \\
\bottomrule
\end{tabularx}

\vspace{0.5em}
\textit{Assessment:} The risk is Cursor or Windsurf exposing their codebase
indexes via MCP. If they do, Quarry still differentiates on document format
diversity, local-first architecture, and agent memory.

\subsection*{Positioning Summary}

No existing tool replicates Quarry's combination: zero-API-key local ONNX
embeddings, 20+ document formats, hybrid search (vector + BM25 via RRF),
agent memory with temporal decay, MCP + CLI surfaces, CUDA acceleration, and
daemon architecture for concurrent agent sessions. The three competitive risks
worth monitoring:

\begin{enumerate}[nosep, leftmargin=2em]
  \item Cursor/Windsurf adding MCP-accessible document search
  \item Khoj or a similar knowledge base shipping an MCP server
  \item A vector DB vendor (Chroma, LanceDB) shipping a batteries-included
        search product on top of their database layer
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
% REFERENCES
% ══════════════════════════════════════════════════════════════════════════════

\newpage
\printbibliography[title={References}]

\end{document}
