%
% architecture.tex
%
% Quarry Technical Architecture Specification
% Written for principal engineers evaluating the system.
%
% Compile: pdflatex architecture.tex
%

\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\lstset{
  basicstyle=\ttfamily\small,
  keywordstyle=\color{blue!80!black},
  commentstyle=\color{green!50!black},
  stringstyle=\color{red!60!black},
  breaklines=true,
  frame=single,
  framerule=0.3pt,
  rulecolor=\color{gray!50},
  backgroundcolor=\color{gray!5},
  columns=fullflexible,
}

\newcommand{\modpath}[1]{\texttt{src/quarry/#1}}
\newcommand{\tool}[1]{\texttt{#1}}
\newcommand{\field}[1]{\texttt{#1}}

\begin{document}

\title{Quarry: Technical Architecture Specification}
\author{Local Semantic Search for AI Agents}
\date{March 2026}
\hypersetup{
  pdftitle={Quarry: Technical Architecture Specification},
  pdfauthor={Punt Labs},
  pdfsubject={Architecture},
  pdfcreator={pdflatex}
}
\maketitle

\tableofcontents
\newpage

% ===================================================================
\section{Overview}
% ===================================================================

Quarry is a local semantic search engine.  It ingests documents in
20+ formats, embeds them with a local ONNX model, stores vectors in
LanceDB, and serves semantic search to AI agents (Claude Code, Claude
Desktop) and a macOS menu bar app.

The system follows the Punt Labs projection strategy: a single core
library projects outward through four thin adapter layers.  Each
surface imports core functions and calls them with resolved arguments.
No intermediary service layer.

\subsection{Design Principles}

\begin{enumerate}[label=\textbf{P\arabic*}.]
  \item \textbf{Library-first.}  The core library does all work.
    CLI, MCP, HTTP, and plugin surfaces are thin wrappers that
    resolve settings and delegate.
  \item \textbf{Local by default.}  Everything runs on the user's
    machine.  No API keys, no cloud accounts.  The embedding model
    downloads once ($\sim$120\,MB, int8 quantized).
  \item \textbf{One daemon, many clients.}  A single
    \texttt{quarry serve} process loads the embedding model once
    and serves all sessions over WebSocket.  Clients connect via
    \texttt{mcp-proxy}.
  \item \textbf{Fire-and-forget I/O.}  Side-effect MCP tools return
    immediately and process in a bounded thread pool.  Search is
    synchronous.
  \item \textbf{Named databases.}  Each database is fully isolated:
    its own LanceDB directory, sync registry, and vector index.
    Work/personal separation without configuration files.
\end{enumerate}

% ===================================================================
\section{System Architecture}
% ===================================================================

\subsection{Deployment Topology}

\textbf{Single machine (localhost TLS):}
\begin{lstlisting}
                    stdio                      wss:// (TLS)
Claude Code <------------------> mcp-proxy <-------------------> quarry serve
             MCP JSON-RPC        (~5 MB Go)   pinned CA cert     (one daemon)
\end{lstlisting}

\textbf{Remote server (GPU):}
\begin{lstlisting}
Mac (client)                                   Linux (server)
                    stdio                       wss:// (TLS)
Claude Code <------------------> mcp-proxy <---------------------> quarry serve
             MCP JSON-RPC        (~5 MB Go)     pinned CA cert     (GPU daemon)

CLI -----> HTTPS GET/POST ---------> quarry serve
           Bearer + pinned CA
\end{lstlisting}

Without the proxy, every Claude Code tab spawns a separate Python
process, each loading the embedding model into $\sim$200\,MB of RAM.
With it, startup is instant and state is shared across all sessions.
Installed services use TLS with TOFU certificate pinning (DES-020)
--- even on localhost.

When a remote server is configured (DES-021), the CLI should route
all data commands over HTTPS to the server, with only authentication
and administration commands remaining local.  As of v1.11.0, only
\texttt{find} and \texttt{status} are remote-routed; remaining
commands are tracked in epic quarry-g0ed.

\subsection{Surface Summary}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Surface} & \textbf{Transport} & \textbf{Purpose} \\
\midrule
CLI         & Direct library calls & Interactive use from terminal \\
MCP server  & stdio or WebSocket   & Claude Code/Desktop tools \\
HTTP server & REST JSON + WS \texttt{/mcp} & Menu bar app + mcp-proxy \\
Plugin      & Hook shell commands  & Auto-register, auto-ingest, compaction safety \\
\bottomrule
\end{tabular}
\end{center}

% ===================================================================
\section{Module Responsibilities}
% ===================================================================

\subsection{Data Layer}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Responsibility} \\
\midrule
Models    & \modpath{models.py}   & Immutable dataclasses: \texttt{PageType}
            enum, \texttt{PageContent}, \texttt{Chunk},
            \texttt{PageAnalysis}.  All \texttt{@dataclass(frozen=True)}. \\
Types     & \modpath{types.py}    & Protocol definitions for external
            dependencies: \texttt{LanceDB}, \texttt{LanceTable},
            \texttt{LanceQuery}, \texttt{ListTablesResult},
            \texttt{OcrBackend}, \texttt{EmbeddingBackend}.
            Structural typing instead of \texttt{Any}. \\
Config    & \modpath{config.py}   & \texttt{Settings} (pydantic
            \texttt{BaseSettings}), \texttt{resolve\_db\_paths()} for
            named databases, ONNX model constants. \\
Database  & \modpath{database.py} & LanceDB operations:
            \texttt{insert\_chunks}, \texttt{search},
            \texttt{list\_documents}, \texttt{delete\_document},
            \texttt{count\_chunks}, etc.  Single table
            \texttt{chunks}. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Ingestion Pipeline}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Responsibility} \\
\midrule
Pipeline    & \modpath{pipeline.py}    & Orchestrator: dispatches by
              format, chunks, embeds, stores.  Entry points:
              \texttt{ingest\_document}, \texttt{ingest\_content},
              \texttt{ingest\_auto} (URL with sitemap discovery). \\
Chunker     & \modpath{chunker.py}     & Text splitting with overlap.
              Respects page boundaries and heading structure. \\
Collections & \modpath{collections.py} & \texttt{derive\_collection()}
              --- determines collection name from path or URL. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Format Processors}

Each processor converts a source format into
\texttt{list[PageContent]}:

\begin{center}
\begin{tabular}{llp{6cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Formats} \\
\midrule
PDF           & \modpath{pdf\_analyzer.py}           & PDF (text via
                PyMuPDF, OCR fallback for image pages) \\
Image         & \modpath{image\_analyzer.py}          & PNG, JPG, TIFF,
                BMP, WebP (OCR) \\
Text          & \modpath{text\_processor.py}          & TXT, MD, LaTeX, DOCX \\
Code          & \modpath{code\_processor.py}          & 30+ languages
                (AST-aware splitting) \\
HTML          & \modpath{html\_processor.py}          & HTML
                (boilerplate stripping, Markdown conversion) \\
Spreadsheet   & \modpath{spreadsheet\_processor.py}   & XLSX, CSV
                (tabular serialization) \\
Presentation  & \modpath{presentation\_processor.py}  & PPTX
                (slide-per-chunk with notes) \\
Dispatcher    & \modpath{text\_extractor.py}          & Extracts text
                from text-based PDF pages (PyMuPDF) \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Backends}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Responsibility} \\
\midrule
Factory     & \modpath{backends.py}    & Thread-safe factory with
              double-checked locking.
              \texttt{get\_ocr\_backend()} and
              \texttt{get\_embedding\_backend()} return cached
              singletons. \\
OCR         & \modpath{ocr\_local.py}  & Local OCR via RapidOCR
              (offline, no setup). \\
Embeddings  & \modpath{embeddings.py}  & Local ONNX embedding
              (snowflake-arctic-embed-m-v1.5, 768-dim, 512
              tokens). \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Sync and Registry}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Responsibility} \\
\midrule
Sync     & \modpath{sync.py}          & Directory sync: discover
           files, compute delta (new/changed/deleted),
           ingest/delete accordingly.
           \texttt{ThreadPoolExecutor} for concurrent ingestion. \\
Registry & \modpath{sync\_registry.py} & SQLite registry of watched
           directories.  Maps directories to collections with
           timestamps. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Surfaces}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Responsibility} \\
\midrule
CLI         & \modpath{\_\_main\_\_.py} & Typer CLI with rich
              formatting.  Synchronous.  All commands: resolve
              settings $\to$ call core $\to$ format output. \\
MCP Server  & \modpath{mcp\_server.py}  & FastMCP server.  Read-only
              tools are synchronous.  Side-effect tools use
              fire-and-forget. \\
HTTP Server & \modpath{http\_server.py} & Starlette ASGI app on
              uvicorn.  REST endpoints + WebSocket \texttt{/mcp}. \\
Hooks       & \modpath{hooks.py}        & Claude Code plugin hooks:
              session-start (auto-register), post-web-fetch
              (auto-ingest), pre-compact (capture transcript).
              All fail-open. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Support}

\begin{center}
\begin{tabular}{llp{7cm}}
\toprule
\textbf{Module} & \textbf{File} & \textbf{Responsibility} \\
\midrule
Formatting & \modpath{formatting.py} & Pre-formatted plain text
             output using unicode box-drawing.  Used by both CLI
             and MCP for consistent output. \\
Results    & \modpath{results.py}    & \texttt{SyncResult} dataclass
             for sync operation reporting. \\
Sitemap    & \modpath{sitemap.py}    & Sitemap discovery and URL
             extraction for web ingestion. \\
Doctor     & \modpath{doctor.py}     & Health checks and install flow:
             model availability, database access, MCP
             configuration, ethos extension setup. \\
\bottomrule
\end{tabular}
\end{center}

% ===================================================================
\section{Daemon Model}
% ===================================================================

\subsection{Why a Daemon}

The embedding model (snowflake-arctic-embed-m-v1.5, int8 quantized
ONNX) occupies $\sim$200\,MB of RAM and takes $\sim$250\,ms to load.
MCP's stdio transport model spawns a new process per session.  Without
a daemon, five Claude Code tabs means five copies of the model in
memory and five cold starts.

\texttt{quarry serve} loads the model once and keeps it resident.
The \texttt{mcp-proxy} binary ($\sim$5\,MB Go binary, $<$10\,ms
startup) bridges each session's MCP stdio to the daemon over
WebSocket.

\subsection{mcp-proxy Architecture}

\texttt{quarry install} downloads \texttt{mcp-proxy} (SHA256-verified,
platform-specific binary) and configures MCP clients to use it.
The proxy:

\begin{enumerate}
  \item Reads MCP JSON-RPC from stdin.
  \item Forwards to \texttt{ws://localhost:8420/mcp} over WebSocket.
  \item Relays responses back to stdout.
\end{enumerate}

Each WebSocket connection gets its own asyncio Task with a
\texttt{ContextVar} for database selection (\texttt{\_db\_name}),
so \texttt{use("work")} in one session does not affect others.

\subsection{CLI Independence}

The CLI does not use the daemon.  \texttt{quarry find "margins"}
loads the embedding model in-process, queries LanceDB, prints
results, and exits.  LanceDB handles concurrent reads safely, so
CLI and daemon can access the same database simultaneously.

% ===================================================================
\section{MCP Tool Surface}
% ===================================================================

\begin{center}
\small
\setlength{\tabcolsep}{4pt}
\begin{longtable}{lp{3.5cm}p{3.2cm}l}
\toprule
\textbf{Tool} & \textbf{Key Parameters} & \textbf{Purpose} &
  \textbf{Exec} \\
\midrule
\endfirsthead
\toprule
\textbf{Tool} & \textbf{Key Parameters} & \textbf{Purpose} &
  \textbf{Exec} \\
\midrule
\endhead
\tool{find}        & \field{query}, \field{limit},
  \field{collection}       & Semantic search            & Sync \\
\tool{ingest}      & \field{source}, \field{overwrite},
  \field{collection}       & Ingest file or URL         & Bg \\
\tool{remember}    & \field{content},
  \field{document\_name}   & Ingest inline text         & Bg \\
\tool{list}        & \field{kind}
                           & List indexed data          & Sync \\
\tool{show}        & \field{document\_name},
  \field{page\_number}     & Document metadata or page  & Sync \\
\tool{delete}      & \field{name}, \field{kind}
                           & Delete document or
                             collection                 & Bg \\
\tool{register\_directory}   & \field{directory},
  \field{collection}       & Register for sync          & Bg \\
\tool{deregister\_directory} & \field{collection},
  \field{keep\_data}       & Remove registration        & Bg \\
\tool{sync\_all}   & ---  & Sync all registered dirs   & Bg \\
\tool{status}      & ---  & Database stats             & Sync \\
\tool{use}         & \field{name}
                           & Switch active database     & Sync \\
\bottomrule
\end{longtable}
\end{center}

Bg = background (\texttt{ThreadPoolExecutor}).

Background tools use a bounded \texttt{ThreadPoolExecutor(max\_workers=4)}.
They return an optimistic response immediately.  Settings and database
connections are snapshotted at the tool boundary and passed into
background functions --- this avoids a race condition where the mutable
\texttt{\_db\_name} ContextVar could change between the tool call and
the background thread's execution.  Exceptions in background threads
are logged via \texttt{logger.exception()}, not raised.

% ===================================================================
\section{HTTP Server}
% ===================================================================

\subsection{ASGI Application}

Starlette app built by \texttt{build\_app()} factory, served by
uvicorn.  REST handlers are sync functions --- Starlette auto-detects
this and runs them in its threadpool.  The \texttt{/mcp} WebSocket
endpoint is async.

Default port: 8420 (\texttt{DEFAULT\_PORT} in \modpath{config.py}),
overridable with \texttt{-{}-port}.

\subsection{Endpoints}

\begin{center}
\begin{tabular}{llp{6cm}l}
\toprule
\textbf{Path} & \textbf{Method} & \textbf{Purpose} &
  \textbf{Auth} \\
\midrule
\texttt{/health}      & GET & \texttt{\{"status":"ok",
  "uptime\_seconds":N\}} & No \\
\texttt{/ca.crt}      & GET & CA certificate PEM (TOFU bootstrap) & No \\
\texttt{/search}      & GET & Hybrid search
  (\field{q}, \field{limit}, \field{collection}, \field{page\_type}, \field{source\_format}, \field{agent\_handle}, \field{memory\_type}) & Yes \\
\texttt{/documents}   & GET & List indexed documents & Yes \\
\texttt{/collections} & GET & List collections & Yes \\
\texttt{/status}      & GET & Database statistics & Yes \\
\texttt{/mcp}         & WS  & MCP JSON-RPC over WebSocket & Yes \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Planned endpoints} (DES-021, epic quarry-g0ed): \texttt{GET /show},
\texttt{POST /ingest}, \texttt{POST /remember}, \texttt{DELETE /documents},
\texttt{DELETE /collections}, \texttt{GET|POST|DELETE /registrations},
\texttt{POST /sync}, \texttt{GET /databases}, \texttt{POST /use}.

\subsection{Port File}

After binding, the server writes the actual port to
\texttt{\~{}/.punt-labs/quarry/data/<db>/serve.port}.  This supports
\texttt{-{}-port 0} (ephemeral assignment).  Removed on shutdown via
lifespan context.

% ===================================================================
\section{Configuration}
% ===================================================================

\subsection{Settings}

All settings are environment variables read via pydantic-settings.

\begin{center}
\small
\setlength{\tabcolsep}{4pt}
\begin{longtable}{llp{6.5cm}}
\toprule
\textbf{Variable} & \textbf{Default} & \textbf{Description} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Default} & \textbf{Description} \\
\midrule
\endhead
\multicolumn{3}{l}{\textbf{Paths}} \\
\midrule
\texttt{QUARRY\_ROOT}    & \texttt{\~{}/.punt-labs/quarry/data} &
  Base directory for all databases \\
\texttt{LANCEDB\_PATH}   & \texttt{<root>/default/lancedb} &
  Vector database location \\
\texttt{REGISTRY\_PATH}  & \texttt{<root>/default/registry.db} &
  Directory sync SQLite database \\
\texttt{LOG\_PATH}        & \texttt{\~{}/.punt-labs/quarry/logs/quarry.log} &
  Log file (rotating, 5\,MB, 3 backups; independent of
  \texttt{QUARRY\_ROOT}) \\
\midrule
\multicolumn{3}{l}{\textbf{Chunking}} \\
\midrule
\texttt{CHUNK\_MAX\_CHARS}     & \texttt{1800} &
  Target max characters per chunk ($\sim$450 tokens) \\
\texttt{CHUNK\_OVERLAP\_CHARS} & \texttt{200} &
  Overlap between consecutive chunks \\
\midrule
\multicolumn{3}{l}{\textbf{Embedding}} \\
\midrule
\texttt{EMBEDDING\_MODEL}     & \texttt{Snowflake/\allowbreak snowflake-arctic-embed-m-v1.5} &
  Model identifier (display only --- the ONNX model is fixed) \\
\texttt{EMBEDDING\_DIMENSION} & \texttt{768} &
  Vector dimension (display only --- fixed at 768) \\
\bottomrule
\end{longtable}
\end{center}

\subsection{Named Databases}

\texttt{resolve\_db\_paths(settings, name)} maps a database name to a
path under \texttt{QUARRY\_ROOT}.  Each database is fully isolated ---
its own LanceDB directory, sync registry, and vector index.  Names containing path separators (\texttt{/} or
\texttt{\textbackslash}) or the literal traversal segments \texttt{.}
or \texttt{..} are rejected; names like \texttt{foo.bar} are allowed.
If \texttt{LANCEDB\_PATH} was explicitly overridden, the override is
preserved.

The persistent default database is stored in
\texttt{\~{}/.punt-labs/quarry/config.toml} as \texttt{[default] database = "name"}.

\subsection{Chunking Tuning}

\textbf{Increase \texttt{CHUNK\_MAX\_CHARS}} (3000--4000) for documents
with long self-contained sections: legal contracts, academic papers,
large source code functions.

\textbf{Decrease \texttt{CHUNK\_MAX\_CHARS}} (800--1200) for dense
documents where each paragraph covers a distinct topic.

\textbf{Increase \texttt{CHUNK\_OVERLAP\_CHARS}} (400) when relevant
information spans paragraph boundaries.

The embedding model has a 512-token context window.  Chunks exceeding
this are truncated during embedding, reducing quality for the tail.

% ===================================================================
\section{Search and Retrieval}
% ===================================================================

\subsection{Embedding Model}

snowflake-arctic-embed-m-v1.5 via ONNX Runtime:

\begin{itemize}
  \item 768-dimensional vectors, 512-token context window
  \item Asymmetric retrieval: queries are prefixed with a search
    instruction, documents are not
  \item int8 quantized ONNX for CPU ($\sim$120\,MB), FP16 for CUDA
    ($\sim$220\,MB)
  \item Provider auto-detection: CUDA+FP16 when available, CPU+int8
    fallback.  \texttt{QUARRY\_PROVIDER} env var overrides
    (\texttt{cpu}, \texttt{cuda}, or unset for auto).
    See DES-016 and \texttt{provider.py}.
  \item Auto-downloads on first use via \texttt{huggingface\_hub}
\end{itemize}

The model is fixed --- there is no configuration to swap it.  Changing
the model invalidates all existing embeddings, requiring full
re-ingestion.

\subsection{OCR}

RapidOCR handles all image-based text extraction.  For semantic
search, OCR accuracy matters less than expected --- the embedding
model is robust to minor OCR errors.  A misspelled word rarely
changes semantic meaning enough to affect search ranking.

\subsection{Search Quality Tips}

\begin{enumerate}
  \item \textbf{Use natural language queries.}  The model is trained on
    question-passage pairs.  ``What were Q3 revenue figures?'' works
    better than ``Q3 revenue.''
  \item \textbf{Use collection filtering.}
    \texttt{quarry find "auth logic" -c backend}.
  \item \textbf{Re-ingest after tuning.}  Chunk parameters only affect
    new ingestions.  Run \texttt{quarry sync} after changes.
  \item \textbf{Check chunk boundaries.}
    \texttt{quarry find -n 1 "query"} and examine the result.
  \item \textbf{Use \texttt{-{}-overwrite} when re-ingesting.}
    Without it, duplicate chunks accumulate.
\end{enumerate}

\subsection{Hybrid Search}

When an \texttt{agent\_handle} filter is provided, quarry uses dual-channel
retrieval instead of vector-only search.

\textbf{Channels:}
\begin{enumerate}
  \item \textbf{Vector similarity} --- existing ANN search via LanceDB
  \item \textbf{BM25 full-text search} --- Tantivy index on the \texttt{text} column, created during schema migration
\end{enumerate}

Results are fused using Reciprocal Rank Fusion (RRF):
\[
  \text{score}(m) = \sum_{\text{channel}} \frac{1}{60 + \text{rank}_{\text{channel}}(m)}
\]

\textbf{Temporal decay} applies to agent-scoped memories (non-empty \texttt{agent\_handle}):
\[
  w = e^{-\lambda \cdot h}
\]
where $\lambda$ is the decay rate and $h$ is hours since ingestion. Unscoped documents ($\texttt{agent\_handle} = \text{``''}$) are exempt from decay.

When no \texttt{agent\_handle} is provided, search uses the existing vector-only path (backwards compatible).

\subsection{Agent Memory Schema}

Three columns extend the chunks table for agent-scoped memory:

\begin{center}
\begin{tabular}{llll}
\textbf{Column} & \textbf{Type} & \textbf{Default} & \textbf{Purpose} \\
\hline
\texttt{agent\_handle} & utf8 & \texttt{""} & Agent identity scope \\
\texttt{memory\_type} & utf8 & \texttt{""} & fact, observation, opinion, procedure \\
\texttt{summary} & utf8 & \texttt{""} & One-line summary \\
\end{tabular}
\end{center}

Migration is idempotent --- \texttt{\_migrate\_schema()} adds missing columns
with empty-string defaults on every table open. Existing databases gain
the columns transparently.

Identity tagging: the PreCompact hook reads the agent handle from
\texttt{.punt-labs/ethos/config.yaml} and tags captured transcripts automatically.

\subsection{Ethos Extension Integration}

Quarry stores its configuration in ethos's generic extension mechanism
(DES-008, DES-019):

\begin{verbatim}
~/.punt-labs/ethos/identities/<handle>.ext/quarry.yaml
\end{verbatim}

The extension file contains two categories of data:

\begin{enumerate}
  \item \textbf{Sidecar config} --- \texttt{memory\_collection} and
    \texttt{expertise\_collections} are read directly by quarry via the
    filesystem (no ethos API call).
  \item \textbf{Session context} --- \texttt{session\_context} is a YAML
    literal block scalar emitted verbatim by ethos at session start and
    before context compaction.  It contains the agent's memory instructions
    (collection name, slash commands, memory types).
\end{enumerate}

\texttt{quarry install} (step 7/7) scans all identity extension directories
and appends \texttt{session\_context} to any \texttt{quarry.yaml} that has
\texttt{memory\_collection} but no \texttt{session\_context}.  Uses raw file
append to preserve existing YAML comments and formatting.  Per-identity
exception handling ensures one malformed file does not abort the rest.

Ownership boundary: ethos emits quarry's instructions without understanding
them.  Quarry writes its own instructions without importing ethos.  The
dependency is one-way --- quarry depends on ethos for identity; ethos has
zero knowledge of quarry's internals.

% ===================================================================
\section{Logging and Exceptions}
% ===================================================================

\subsection{Logging Standard}

Every module that performs I/O declares
\texttt{logger = logging.getLogger(\_\_name\_\_)}.  Pure data modules
(\texttt{models.py}, \texttt{types.py}, \texttt{chunker.py}) do not.

Logging is configured once at the application entry point (CLI or MCP
server).  Library modules never call \texttt{logging.basicConfig}.

\begin{center}
\begin{tabular}{lp{8cm}}
\toprule
\textbf{Level} & \textbf{Use} \\
\midrule
\texttt{DEBUG}   & Internal state: variable values, branch decisions,
                   intermediate results. \\
\texttt{INFO}    & Operational milestones: starting a job, completing
                   a step, resource counts. \\
\texttt{WARNING} & Unexpected but recoverable: empty input, deprecated
                   parameter usage. \\
\texttt{ERROR}   & Failures that prevent completion but do not crash.
                   Always with exception context. \\
\bottomrule
\end{tabular}
\end{center}

\texttt{CRITICAL} is not used.  If the process must exit, it raises an
exception.

Log messages use \texttt{\%s}-style formatting (lazy evaluation), not
f-strings.  Each message includes enough context to trace an operation
without reading code.

\subsection{Exception Handling}

The codebase uses built-in exception types.  No custom exceptions
unless a caller needs to distinguish failure modes programmatically.

\begin{center}
\begin{tabular}{lp{8cm}}
\toprule
\textbf{Exception} & \textbf{Raised when} \\
\midrule
\texttt{ValueError}       & Invalid input: unsupported format, bad
                            parameter. \\
\texttt{FileNotFoundError} & A file path argument does not exist. \\
\texttt{RuntimeError}      & An operation reports failure (OCR engine
                            error, ingestion failure). \\
\texttt{TimeoutError}      & An external service exceeds its time
                            budget. \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Rules:}

\begin{enumerate}
  \item Never swallow exceptions.  Every \texttt{except} block must
    re-raise, or log with \texttt{logger.exception()} and raise a
    different exception, or (at system boundaries only) return a
    documented sentinel.
  \item Never use bare \texttt{except:}.
  \item Never catch \texttt{Exception} broadly in library code.  Broad
    catches are permitted only at the outermost boundary (MCP tool
    handler, CLI command).
  \item Exceptions carry context: include the values that caused the
    failure.
  \item Use \texttt{try/finally} for cleanup, not
    \texttt{try/except}.
  \item Do not use exceptions for flow control.
\end{enumerate}

% ===================================================================
\section{Security}
% ===================================================================

\subsection{Bearer Token Authentication}

\texttt{quarry serve -{}-api-key} (or \texttt{QUARRY\_API\_KEY} env var)
gates all HTTP endpoints except \texttt{/health} behind
\texttt{Authorization: Bearer <key>}.

\begin{itemize}
  \item \texttt{/health} is exempt --- load balancers need
    unauthenticated health checks.
  \item \texttt{OPTIONS} is exempt --- CORS preflight requests carry
    no auth.
  \item \texttt{hmac.compare\_digest} for token comparison ---
    prevents timing attacks.
  \item Case-insensitive scheme per RFC~7235.
  \item Empty key = no auth --- prevents accidental trivial bypass.
  \item No key = auth disabled --- local use requires no key.
\end{itemize}

The server refuses to bind to a non-loopback address without
\texttt{-{}-api-key}.

\subsection{WebSocket Security (CSWSH)}

Origin-based cross-site WebSocket hijacking protection:

\begin{itemize}
  \item If an \texttt{Origin} header is present, it must match the
    CORS allow-list.
  \item Browsers always send \texttt{Origin}; non-browser clients
    like \texttt{mcp-proxy} do not.
  \item Bearer auth is checked before WebSocket accept (close code
    1008 on failure).
\end{itemize}

\subsection{CORS}

\texttt{CORSMiddleware} configured with GET and OPTIONS methods,
Authorization and Content-Type headers.  Default allowed origin:
\texttt{http://localhost}.  Configurable via \texttt{-{}-cors-origin}
(repeatable).

The server reflects the request's \texttt{Origin} header only when it
matches the allow list, and adds \texttt{Vary: Origin} to signal
cacheability varies by origin.  When no \texttt{Origin} is present,
no CORS headers are emitted.

\subsection{TLS and TOFU Certificate Pinning}

The installed service always runs with TLS enabled.  \texttt{quarry
serve} without \texttt{-{}-tls} is supported for local development but
must not be used for production.  Certificate management uses TOFU
(Trust On First Use) with self-signed CA pinning (DES-020).

\textbf{Certificate generation:} \texttt{quarry install} generates
an EC~P-256 CA and server certificate.  Files are written atomically
to \texttt{\~{}/.punt-labs/quarry/tls/} with restricted permissions
(0600 for keys, 0644 for CA cert).  The server cert SAN includes the
configured hostname (via \texttt{QUARRY\_TLS\_HOSTNAME}), localhost,
and loopback addresses.

\textbf{TOFU login:}
\begin{enumerate}
  \item Client fetches \texttt{/ca.crt} over HTTPS (verification
    disabled --- bootstrap).
  \item Displays SHA256 fingerprint for out-of-band confirmation.
  \item Pins CA cert at
    \texttt{\~{}/.punt-labs/mcp-proxy/quarry-ca.crt}.
  \item All subsequent connections verify against the pinned CA only
    --- system roots excluded.
\end{enumerate}

\textbf{mcp-proxy:} The \texttt{quarry.toml} profile includes
\texttt{ca\_cert} pointing to the pinned CA.  mcp-proxy builds a
custom \texttt{tls.Config} with the pinned CA as the sole root,
enforcing TLS~1.3 minimum.

\subsection{Log Safety (CWE-532, CWE-117)}

Uvicorn's access log is disabled (\texttt{access\_log=False}),
eliminating query string leakage at the source.  The search handler
logs only result count, never the raw query.  WebSocket session keys
are sanitized before logging: control characters stripped via
\texttt{\_CONTROL\_CHAR\_RE} and truncated to 64 characters to prevent
log injection (CWE-117) and log flooding.

% ===================================================================
\section{Deployment}
% ===================================================================

\subsection{Single Machine}

\begin{lstlisting}
curl -fsSL https://raw.githubusercontent.com/.../install.sh | sh
\end{lstlisting}

Installs quarry, embedding model, mcp-proxy, Claude Code plugin, and
registers a daemon with TLS on localhost.

\subsection{Server (Remote GPU)}

\begin{lstlisting}
curl -fsSL https://raw.githubusercontent.com/.../install.sh | sh -s -- --server
\end{lstlisting}

No Claude Code required.  Installs quarry, embedding model, generates
TLS certificates, registers systemd service on \texttt{0.0.0.0:8420}.
Detects NVIDIA GPUs and swaps \texttt{onnxruntime} for
\texttt{onnxruntime-gpu}.  Prints CA fingerprint for client TOFU.

\subsection{Client (Remote Access)}

\begin{lstlisting}
curl -fsSL https://raw.githubusercontent.com/.../install.sh | sh -s -- --client
quarry login <server> --api-key <token>
\end{lstlisting}

No model download, no daemon.  Installs CLI, mcp-proxy, and Claude
Code plugin.  \texttt{quarry login} performs TOFU certificate pinning
and writes the mcp-proxy config.

\subsection{Daemon (\texttt{quarry serve})}

\begin{lstlisting}
QUARRY_API_KEY=<token> quarry serve --port 8420 --host 0.0.0.0 --tls
\end{lstlisting}

Non-loopback hosts require an API key (the server refuses to start
without one).

Managed by \texttt{launchd} (macOS) or \texttt{systemd} (Linux) via
\texttt{quarry install}.  API key delivered via systemd
\texttt{EnvironmentFile} (Linux) or launchd
\texttt{EnvironmentVariables} (macOS) --- never in process arguments.

\subsection{Container (Fly.io)}

Multi-stage Dockerfile, three stages:

\begin{enumerate}
  \item \textbf{deps} (\texttt{python:3.13-slim}): installs
    \texttt{uv}, runs \texttt{uv sync -{}-frozen -{}-no-dev}.  Two-pass
    for Docker layer caching (deps first, then source).
  \item \textbf{model} (extends \texttt{deps}): downloads the
    embedding model at build time ($\sim$120\,MB, int8 quantized).
    Cached as a separate Docker layer.
  \item \textbf{runtime} (\texttt{python:3.13-slim}): copies
    \texttt{/app} from deps, copies model cache from model stage.
    \texttt{QUARRY\_ROOT=/data}, port 8080.
\end{enumerate}

LanceDB data lives on a Fly persistent volume at \texttt{/data}.
\texttt{QUARRY\_API\_KEY} is set via \texttt{fly secrets}.
Cold start is $\sim$5\,s with the baked-in model.

% ===================================================================
\section{Performance}
% ===================================================================

\subsection{Critical Path}

\begin{center}
\begin{tabular}{lrl}
\toprule
\textbf{Operation} & \textbf{Latency} & \textbf{Notes} \\
\midrule
Model load         & $\sim$250\,ms & One-time per process \\
Embedding (1 chunk) & $\sim$50\,ms  & Apple Silicon, CPU \\
LanceDB search     & $<$10\,ms     & Vector similarity + filter \\
End-to-end search  & $<$100\,ms    & After model is loaded \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Fire-and-Forget MCP Pattern}

Side-effect MCP tools return immediately and process in a bounded
thread pool (4 workers).  This is necessary because:

\begin{enumerate}
  \item MCP tool calls block the LLM's response stream.  A 30-second
    ingest blocks Claude from responding.
  \item The bounded pool prevents resource exhaustion under concurrent
    requests.
  \item Settings and database connections are snapshotted at the tool
    boundary, avoiding race conditions with the mutable
    \texttt{\_db\_name} ContextVar.
\end{enumerate}

\subsection{Single Table Design}

All chunks live in one LanceDB table (\texttt{chunks}).  Document and
collection boundaries are columns, not separate tables.  This
simplifies cross-document search and avoids table proliferation.
Filtering by document/collection/page\_type/source\_format uses
LanceDB's built-in filter predicates on the vector search.

% ===================================================================
\section{Plugin and Hook System}
% ===================================================================

The Claude Code plugin (\texttt{.claude-plugin/}) registers hooks
that fire on session events and tool calls.  All hooks are fail-open:
exceptions are logged and the process exits~0.

\begin{center}
\begin{tabular}{llp{5cm}l}
\toprule
\textbf{Hook Event} & \textbf{Matcher} & \textbf{Effect} &
  \textbf{Blocks?} \\
\midrule
SessionStart  & * & Auto-register directory + background sync &
  No \\
PostToolUse   & quarry tools & Suppress tool output formatting &
  No \\
PostToolUse   & WebFetch & Auto-ingest fetched URL &
  No \\
PreCompact    & * & Capture transcript as session notes &
  No \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Session Start}

\texttt{handle\_session\_start()} auto-registers the working directory
and launches a background sync via a detached subprocess.  Uses
atomic PID-file locking (\texttt{O\_CREAT|O\_EXCL}) at
\texttt{\~{}/.punt-labs/quarry/sync.pid} to prevent concurrent syncs.  Returns
\texttt{additionalContext} immediately without waiting.

\subsection{Web Fetch Capture}

\texttt{handle\_post\_web\_fetch()} ingests URLs fetched during a
session into the \texttt{web-captures} collection.  Deduplicates by
document name.  Prefers already-fetched content from the tool response
(avoids re-fetch, reduces SSRF surface).

\subsection{Pre-Compact Capture}

\texttt{handle\_pre\_compact()} reads the transcript (JSONL) and
ingests it into the \texttt{session-notes} collection.  Extracts
user/assistant message text, skipping tool-use blocks.  Capped at
500{,}000 characters.

% ===================================================================
\section{CLI Commands}
% ===================================================================

\begin{center}
\begin{longtable}{lp{8cm}}
\toprule
\textbf{Command} & \textbf{Purpose} \\
\midrule
\endfirsthead
\toprule
\textbf{Command} & \textbf{Purpose} \\
\midrule
\endhead
\texttt{ingest <source>}      & Ingest file or URL.  Flags: \texttt{-{}-agent-handle},
  \texttt{-{}-memory-type}, \texttt{-{}-summary} \\
\texttt{remember}             & Ingest stdin content \\
\texttt{find <query>}         & Semantic search \\
\texttt{show <document>}      & Document metadata or page text \\
\texttt{status}               & Database statistics \\
\texttt{use <name>}           & Set persistent default database \\
\texttt{delete <name>}        & Delete document or collection \\
\texttt{register <directory>} & Register for incremental sync \\
\texttt{deregister <collection>} & Remove directory registration \\
\texttt{sync}                 & Sync all registered directories \\
\texttt{list documents}       & List indexed documents \\
\texttt{list collections}     & List collections with counts \\
\texttt{list databases}       & List named databases \\
\texttt{list registrations}   & List registered directories \\
\texttt{serve}                & Start HTTP API server \\
\texttt{mcp}                  & Start MCP server (stdio) \\
\texttt{login <host>}         & TOFU login to remote server (cert pinning) \\
\texttt{logout}              & Disconnect from remote server \\
\texttt{remote list}         & Show remote config; \texttt{-{}-ping} validates connection \\
\texttt{install}             & Set up data directory, download model, generate TLS certs,
  register daemon, detect GPU, configure ethos ext \\
\texttt{doctor}              & Check environment health \\
\texttt{uninstall}           & Remove system daemon \\
\texttt{version}             & Print version \\
\bottomrule
\end{longtable}
\end{center}

Global flags: \texttt{-{}-json}, \texttt{-{}-verbose}/\texttt{-v},
\texttt{-{}-quiet}/\texttt{-q}, \texttt{-{}-db <name>}.

\textbf{Remote routing (DES-021):} When a remote server is configured
(via \texttt{quarry login}), all data commands should route to the
remote server over HTTPS with the pinned CA cert.  Only authentication
commands (\texttt{login}, \texttt{logout}, \texttt{remote}) and
administration commands (\texttt{install}, \texttt{uninstall},
\texttt{serve}, \texttt{mcp}, \texttt{version}) are local-only.
As of v1.11.0, only \texttt{find} and \texttt{status} are
remote-routed; remaining commands (including \texttt{doctor}) are
tracked in epic quarry-g0ed.

% ===================================================================
\section{Test Architecture}
% ===================================================================

821 tests across 33 files.  Three tiers plus integration:

\begin{center}
\begin{tabular}{lp{5cm}p{5cm}}
\toprule
\textbf{Tier} & \textbf{Strategy} & \textbf{Files} \\
\midrule
Tier 1: Core logic & Real data, no mocks & \texttt{test\_database},
  \texttt{test\_chunker}, \texttt{test\_embeddings},
  \texttt{test\_code\_processor}, \texttt{test\_html\_processor},
  \texttt{test\_text\_processor}, \texttt{test\_collections},
  \texttt{test\_config}, \texttt{test\_formatting},
  \texttt{test\_image\_analyzer}, \texttt{test\_latex\_utils},
  \texttt{test\_models}, \texttt{test\_pdf\_analyzer},
  \texttt{test\_presentation\_processor},
  \texttt{test\_spreadsheet\_processor},
  \texttt{test\_text\_extractor},
  \texttt{test\_registry} (17 files) \\
Tier 2: Orchestration & Mocked I/O & \texttt{test\_pipeline},
  \texttt{test\_pipeline\_images},
  \texttt{test\_ocr\_local}, \texttt{test\_url\_ingestion},
  \texttt{test\_sitemap}, \texttt{test\_backends},
  \texttt{test\_sync},
  \texttt{test\_hooks}, \texttt{test\_doctor} (9 files) \\
Tier 3: Surface wiring & Fully mocked, $<$2\,s &
  \texttt{test\_cli}, \texttt{test\_mcp\_server},
  \texttt{test\_mcp\_websocket}, \texttt{test\_http\_server},
  \texttt{test\_proxy}, \texttt{test\_service} (6 files) \\
Integration & Real ONNX + real LanceDB &
  \texttt{test\_integration} (\texttt{@pytest.mark.slow}) \\
\bottomrule
\end{tabular}
\end{center}

Quality gates: \texttt{ruff} (lint + format), \texttt{mypy} (strict),
\texttt{pyright} (strict), \texttt{pytest} (all markers except
slow/integration).  Zero violations required.

% ===================================================================
\section{Formal Model}
% ===================================================================

The plugin state machine --- how quarry hooks into the Claude Code
session lifecycle --- is formally specified in
\texttt{docs/claude-code-quarry.tex} using Z notation (ISO~13568).

The specification covers:

\begin{itemize}
  \item Session start with/without auto-sync
  \item Web fetch auto-capture into \texttt{web-captures} collection
  \item Pre-compaction transcript capture into \texttt{session-notes}
  \item Database switching via \texttt{use} tool
  \item Knowledge hint injection at tool boundaries
  \item Compaction observability: a capture flag records whether
    capture preceded compaction; the hook system enforces
    capture-before-compaction on a best-effort basis
  \item Clean session boundaries: all quarry state cleared on
    \texttt{EndSession}
\end{itemize}

The specification can be type-checked with \texttt{fuzz -t
claude-code-quarry.tex}.

\end{document}
